---
title: "GSE analysis based on list of genes directly regulated by NF-kB"
author: "Juraj Michalik"
date: "2023-12-08"
output: html_document
---

LICENCE: MIT (see LICENCE.md)

Supplementary analysis using data (notably NF-kB target genes) from this paper: https://www.nature.com/articles/s41590-023-01561-7#Sec28

# Setup

Load required packages.

```{r, include = F}
knitr::opts_chunk$set(echo = FALSE)

library(DESeq2)
library(dplyr)
library(tibble)
library(ggrepel)
library(magrittr)
library(clusterProfiler)
library(fgsea)
library(pheatmap)
library(dichromat)
library(limma)
library(DT)

# annotation libs
library(AnnotationHub)

dir.create(file.path('GSEA_tables/'), showWarnings = F)

col_WT <- '#55a0fbff'
col_GTKO <- '#c000c0ff'
```

Function for reannotation and PCA.

```{r}
# Get current Mus Musculus database from AnnotationHub if not downloaded already
getEnsMm106 <- function(){
  aHu <- AnnotationHub()
  aHuQuery <- query(aHu, pattern = c("Mus Musculus", "EnsDb", '106'))
  EnsMm106 <- aHuQuery[[1]]
  return(EnsMm106)
}

# adds annotation to object
reannotate <- function(dds.obj, keyslist = row.names(dds.obj)){
  EnsMm106 <- getEnsMm106()
  symbol.vector <- mapIds(EnsMm106,
                          keys = row.names(dds.obj),
                          column = "SYMBOL",
                          keytype = "GENEID",
                          multiVals = "first")
  # rename only if symbol is a thing
  row.names(dds.obj) <- ifelse(is.na(symbol.vector) | symbol.vector == '', row.names(dds.obj), symbol.vector)
  return(dds.obj)    
}


# returns PCA data with more PCs (12 I think)
get.complete.PCA.data <- function(dds.obj, ntop = 500){
	rvar <- rowVars(assay(dds.obj))
	select <- order(rvar, decreasing=TRUE)[seq_len(min(ntop, length(rvar)))]
	pca.dat <- prcomp(t(assay(dds.obj)[select,]))
	return(pca.dat)
}
```

# GSEA tests

Here we will perform GSEA analysis on set of genes that are target for NFkB from the paper above. For this purpose we load required genes first.

```{r}
NFkB_target_genes_I1 <- read.csv('Paper_I1_cluster.csv', h=T)[,1]

NFkB_target_genes_I2 <- read.csv('Paper_I2_cluster.csv', h=T)[,1]

NFkB_target_genes_I3 <- read.csv('Paper_I3_cluster.csv', h=T)[,1]

NFkB_target_genes_I6 <- read.csv('Paper_I6_cluster.csv', h=T)[,1]

NFkB_target_genes <- list(NFkB_target_genes_I1, NFkB_target_genes_I2, NFkB_target_genes_I3, NFkB_target_genes_I6)
names(NFkB_target_genes) <- c('I1', 'I2', 'I3', 'I6')
```

First we need to calculate contrast for exp1 between activated and non-activated cells because we don't have that from previous case. We therefore load counts and create new DESeq2 object.

```{r}
expcounts_1 <- readRDS('Rds_data/exp1_counts.rds')
expcounts_1$Activation.bin <- ifelse(expcounts_1$Activation == 'non-act', 'non-act', 'act')

dds_exp1_alt <- DESeqDataSet(expcounts_1, design = ~ Experiment + Activation.bin + Knockout)
rowData(dds_exp1_alt)$EnsemblID <- rownames(expcounts_1)
dds_exp1_alt <- dds_exp1_alt[rowSums(counts(dds_exp1_alt)) > 10, ] # remove <= 10 counts = noise
dds_exp1_alt <- reannotate(dds_exp1_alt)
```

Run DESeq.

```{r}
dds_exp1_alt <- DESeq(dds_exp1_alt)
```

Run DESeq, then get results for 'activated' vs. 'non-activated contrast'.

```{r}
res_exp1_act_vs_non_act <- lfcShrink(dds = dds_exp1_alt, contrast = c('Activation.bin', 'act', 'non-act'), type = 'ashr')
```

Now load previously completed results.

```{r}
res_exp1_act_KO_vs_WT <- readRDS('Rds_data/exp1_res_KO_vs_WT_act_only.rds')
res2_act_exp2_act_KO_vs_WT <- readRDS('Rds_data/exp2_res_KO_vs_WT_act_only.rds')
```

Make ranked list for each.

```{r}
ranked_exp1_all <- res_exp1_act_vs_non_act$log2FoldChange
names(ranked_exp1_all) <- rownames(res_exp1_act_vs_non_act)

ranked_exp1_act <- res_exp1_act_KO_vs_WT$log2FoldChange
names(ranked_exp1_act) <- rownames(res_exp1_act_KO_vs_WT)

ranked_exp2_act <- res2_act_exp2_act_KO_vs_WT$log2FoldChange
names(ranked_exp2_act) <- rownames(res2_act_exp2_act_KO_vs_WT)
```

Now do GSEA.

```{r, include = F}
set.seed(42)
fgsea_exp1_all <- fgsea(pathways = NFkB_target_genes,
                        stats = ranked_exp1_all,
                        nperm=500000)

fgsea_exp1_act <- fgsea(pathways = NFkB_target_genes,
                        stats = ranked_exp1_act,
                        nperm=500000)

fgsea_exp2_act <- fgsea(pathways = NFkB_target_genes,
                        stats = ranked_exp2_act,
                        nperm=500000)
```

Plot all for cluster I3 first.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I3']], ranked_exp1_all)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_1_I3 <- plotEnrichment(NFkB_target_genes[['I3']],
               ranked_exp1_all) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_all$padj[3], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_all$NES[3], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ',fgsea_exp1_all$size[3]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I3 cluster (direct target of NF-kB)\n for contrast of Activated vs. Non-Activated - Mice (Exp1, all)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_1_I3)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I3']], ranked_exp1_act)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_2_I3 <- plotEnrichment(NFkB_target_genes[['I3']],
               ranked_exp1_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_act$padj[3], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_act$NES[3], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp1_act$size[3]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I3 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT - Mice (Exp1, activ. only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_2_I3)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I3']], ranked_exp2_act)$data

xcoord <- min(GSE_data$x) * 0.2
yrange <- min(GSE_data$y) - max(GSE_data$y)
ycoord1 <- yrange * 0.9 + max(GSE_data$y)
ycoord2 <- yrange * 0.8 + max(GSE_data$y)
ycoord3 <- yrange * 0.7 + max(GSE_data$y) 
  
GSEA_nfkb_3_I3 <- plotEnrichment(NFkB_target_genes[['I3']],
               ranked_exp2_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp2_act$padj[3], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp2_act$NES[3], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp2_act$size[3]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I3 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT - Mice (Exp2, activ. only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_3_I3)
```

Save all of the above.

```{r}
tiff('Figures/NFkB_Figures/exp1_all_NFkB_I3_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_1_I3)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures/exp1_act_NFkB_I3_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_2_I3)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures/exp2_act_NFkB_I3_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_3_I3)
dev.off()
```

Now do this for clusters I1, I2 and I6. I1 first.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I1']], ranked_exp1_all)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_1_I1 <- plotEnrichment(NFkB_target_genes[['I1']],
               ranked_exp1_all) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_all$padj[1], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_all$NES[1], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ',fgsea_exp1_all$size[1]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I1 cluster (direct target of NF-kB)\n for contrast of Activated vs. Non-Activated - Mice (Exp1, all)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_1_I1)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I1']], ranked_exp1_act)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_2_I1 <- plotEnrichment(NFkB_target_genes[['I1']],
               ranked_exp1_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_act$padj[1], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_act$NES[1], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp1_act$size[1]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I1 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT - Mice (Exp1, activ. only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_2_I1)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I1']], ranked_exp2_act)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_3_I1 <- plotEnrichment(NFkB_target_genes[['I1']],
               ranked_exp2_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp2_act$padj[1], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp2_act$NES[1], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp2_act$size[1]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I1 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT - Mice (Exp2, activ. only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_3_I1)
```

Save all of the above.

```{r}
tiff('Figures/NFkB_Figures/exp1_all_NFkB_I1_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_1_I1)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures/exp1_act_NFkB_I1_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_2_I1)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures/exp2_act_NFkB_I1_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_3_I1)
dev.off()
```

Cluster I2.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I2']], ranked_exp1_all)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_1_I2 <- plotEnrichment(NFkB_target_genes[['I2']],
               ranked_exp1_all) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_all$padj[2], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_all$NES[2], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ',fgsea_exp1_all$size[2]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I2 cluster (direct target of NF-kB)\n for contrast of Activated vs. Non-Activated - Mice (Exp1, all)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_1_I2)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I2']], ranked_exp1_act)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_2_I2 <- plotEnrichment(NFkB_target_genes[['I2']],
               ranked_exp1_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_act$padj[2], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_act$NES[2], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp1_act$size[2]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I2 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT - Mice (Exp1, activ. only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_2_I2)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I2']], ranked_exp2_act)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_3_I2 <- plotEnrichment(NFkB_target_genes[['I2']],
               ranked_exp2_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp2_act$padj[2], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp2_act$NES[2], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp2_act$size[2]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I2 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT - Mice (Exp2, activ. only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_3_I2)
```

Save all of the above.

```{r}
tiff('Figures/NFkB_Figures/exp1_all_NFkB_I2_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_1_I2)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures/exp1_act_NFkB_I2_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_2_I2)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures/exp2_act_NFkB_I2_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_3_I2)
dev.off()
```

Cluster I6.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I6']], ranked_exp1_all)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_1_I6 <- plotEnrichment(NFkB_target_genes[['I6']],
               ranked_exp1_all) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_all$padj[4], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_all$NES[4], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ',fgsea_exp1_all$size[4]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I6 cluster (direct target of NF-kB)\n for contrast of Activated vs. Non-Activated - Mice (Exp1, all)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_1_I6)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I6']], ranked_exp1_act)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_2_I6 <- plotEnrichment(NFkB_target_genes[['I6']],
               ranked_exp1_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_act$padj[4], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_act$NES[4], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp1_act$size[4]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I6 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT - Mice (Exp1, activ. only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_2_I6)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I6']], ranked_exp2_act)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_3_I6 <- plotEnrichment(NFkB_target_genes[['I6']],
               ranked_exp2_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp2_act$padj[4], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp2_act$NES[4], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp2_act$size[4]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I6 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT - Mice (Exp2, activ. only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_3_I6)
```

Save all of the above.

```{r}
tiff('Figures/NFkB_Figures/exp1_all_NFkB_I6_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_1_I6)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures/exp1_act_NFkB_I6_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_2_I6)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures/exp2_act_NFkB_I6_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_3_I6)
dev.off()
```

# Just WT from first case

Make deseq with WT only.

```{r}
expcounts_1 <- readRDS('Rds_data/exp1_counts.rds')
expcounts_1$Activation.bin <- ifelse(expcounts_1$Activation == 'non-act', 'non-act', 'act')

dds_exp1_WT <- DESeqDataSet(expcounts_1[,expcounts_1$Knockout == 'WT'], design = ~ Experiment + Activation.bin)
rowData(dds_exp1_WT)$EnsemblID <- rownames(expcounts_1[,expcounts_1$Knockout == 'WT'])
dds_exp1_WT <- dds_exp1_WT[rowSums(counts(dds_exp1_WT)) > 10, ] # remove <= 10 counts = noise
dds_exp1_WT <- reannotate(dds_exp1_WT)
```

Run DESeq.

```{r}
dds_exp1_WT <- DESeq(dds_exp1_WT)
```

Run DESeq, then get results for 'activated' vs. 'non-activated contrast'.

```{r}
res_exp1_WT_act_vs_non_act <- lfcShrink(dds = dds_exp1_WT, contrast = c('Activation.bin', 'act', 'non-act'), type = 'ashr')
```

Make ranked list.

```{r}
ranked_exp1_WT <- res_exp1_WT_act_vs_non_act$log2FoldChange
names(ranked_exp1_WT) <- rownames(res_exp1_WT_act_vs_non_act)
```

Now do GSEA.

```{r, include = F}
set.seed(42)
fgsea_exp1_WT <- fgsea(pathways = NFkB_target_genes,
                       stats = ranked_exp1_WT,
                       nperm=500000)
```

Plot all.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I3']], ranked_exp1_WT)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_4 <- plotEnrichment(NFkB_target_genes[['I3']],
               ranked_exp1_WT) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_WT$padj[3], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_WT$NES[3], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp1_WT$size[3]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I3 cluster (direct target of NF-kB)\n for contrast of Activated vs. Non-Activated - Mice (Exp1, WT only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_4)
```

```{r}
tiff('Figures/NFkB_Figures/exp1_WT_NFkB_I3_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_4)
dev.off()
```

# Scatter plot of combined sets

Here we combine data from results from exp1 - activated and exp2 - activated based on symbols.

```{r}
res_exp2_act <- readRDS('Rds_data/exp2_res_KO_vs_WT_act_only.rds')
```

```{r}
combined_data <- as.data.frame(res_exp1_act_KO_vs_WT) %>% rownames_to_column('symbol') %>%
  dplyr::inner_join(as.data.frame(res_exp2_act) %>% rownames_to_column('symbol'), by = c('symbol' = 'symbol'), suffix = c(".exp1", ".exp2"))

combined_data <- combined_data %>% dplyr::filter(symbol %in% NFkB_target_genes[['I3']])
```

Plot scatter.

```{r}
pp <- nrow(combined_data[combined_data$log2FoldChange.exp1 > 0 & combined_data$log2FoldChange.exp2 > 0,])
pn <- nrow(combined_data[combined_data$log2FoldChange.exp1 > 0 & combined_data$log2FoldChange.exp2 <= 0,])
nn <- nrow(combined_data[combined_data$log2FoldChange.exp1 <= 0 & combined_data$log2FoldChange.exp2 <= 0,])
np <- nrow(combined_data[combined_data$log2FoldChange.exp1 <= 0 & combined_data$log2FoldChange.exp2 > 0,])
```

```{r}
scatter_plot_combin <- ggplot(combined_data, aes(x = log2FoldChange.exp1, y = log2FoldChange.exp2, label = symbol)) +
  geom_point(col = 'red') + 
  geom_text_repel(max.overlaps = 5, seed = 10) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  geom_vline(xintercept = 0, linetype = 'dashed') +
  theme_classic() +
  xlab('L2FC (GTKO vs. WT) - Exp1 act.') +
  ylab('L2FC (GTKO vs. WT) - Exp2 act.') +
  annotate('text', x = 0.3, y = -0.5, label = paste0('L2FC.exp1>0, L2FC.exp2>0: ', pp, 
                                                    '\nL2FC.exp1>0, L2FC.exp2<=0: ', pn,
                                                    '\nL2FC.exp1<=0, L2FC.exp2<=0: ', nn,
                                                    '\nL2FC.exp1<=0, L2FC.exp2>0: ', np), hjust = 0, col = 'red') +
  ggtitle('Comparison between L2FC values between GTKO and WT mice expression\n between Exp1 and Exp2 (act. cells only for both)')
print(scatter_plot_combin)
```

```{r}
tiff('Figures/NFkB_Figures/exp1_exp2_act_scatter_GTKO_vs_WT_NFkB.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(scatter_plot_combin)
dev.off()
```

# GSEA between activated and inhibited cells of exp2

Here we load data from exp2 that compare activated and inhibited cells.

```{r}
dds_exp2 <- readRDS('Rds_data/exp2_DESeq_all.rds')
res_exp2_act_vs_inh <- readRDS('Rds_data/exp2_res_Act_vs_Inh.rds')
```

Make ranked list for each.

```{r}
ranked_exp2_all <- res_exp2_act_vs_inh$log2FoldChange
names(ranked_exp2_all) <- rownames(res_exp2_act_vs_inh)
```

Now do GSEA.

```{r, include = F}
set.seed(42)
fgsea_exp2_all <- fgsea(pathways = NFkB_target_genes,
                        stats = ranked_exp2_all,
                        nperm=500000)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I3']], ranked_exp2_all)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_5 <- plotEnrichment(NFkB_target_genes[['I3']],
               ranked_exp2_all) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp2_all$padj[3], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp2_all$NES[3], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp2_all$size[3]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I3 cluster (direct target of NF-kB)\n for contrast of Activated vs. P38 Inhibited - Mice (Exp2, all)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_5)
```

```{r}
tiff('Figures/NFkB_Figures/exp2_all_NFkB_I3_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_5)
dev.off()
```

Heatmap of exp2.

```{r}
rlog_exp2 <- readRDS('Rds_data/exp2_rlog.rds')
```

```{r}
colfunc <- colorRampPalette(c('steelblue', "gray90", 'firebrick'))
vis_genes <- intersect(NFkB_target_genes[['I3']], rownames(rlog_exp2))
vis_genes_tab <- limma::removeBatchEffect(assay(rlog_exp2)[vis_genes,], colData(rlog_exp2)$Experiment)

tiff('Figures/NFkB_Figures/exp2_heatmap_NF-kB.tiff', units = 'in', width = 6.5, height = 15.5, res = 150)

pheatmap(vis_genes_tab, border = 'NA', scale = 'row', color=colfunc(64), cluster_rows = T,
         annotation_col = as.data.frame(colData(dds_exp2)[c('Activation', 'Knockout')]), cluster_cols = F,
         main='Heatmap of NF-kB target genes between GTKO \n and WT, Activated and Inhibited mice (Exp2)', cex = 1,
         annotation_colors = list(Knockout = c(GTKO = col_GTKO, WT = col_WT), Activation = c(Act = 'green2', Act_and_p38i = 'orange')))

dev.off()
```

# Combined analysis for activated cells from exp1 and exp2 activated cells only

Load counts from both tables.

```{r}
count_table_1 <- readRDS('Rds_data/exp1_counts.rds')
count_table_2 <- readRDS('Rds_data/exp2_counts.rds')

dds_exp1 <- readRDS('Rds_data/exp1_DESeq_all.rds')
dds_exp2 <- readRDS('Rds_data/exp2_DESeq_all.rds')

colData_exp1 <- colData(dds_exp1)
colData_exp2 <- colData(dds_exp2)
```

Combine coldata and counts, then add number of experiment.

```{r}
count_table_bound <- cbind(assay(count_table_1), assay(count_table_2))

colData_exp1$Experiment <- paste(colData_exp1$Experiment, 1, sep = '_')
colData_exp2$Experiment <- paste(colData_exp2$Experiment, 2, sep = '_')

colData_exp1$Batch <- '1'
colData_exp2$Batch <- '2'
  
colData_bound <- rbind(colData_exp1, colData_exp2)
colData_bound <- colData_bound %>% as.data.frame %>% dplyr::select(-sizeFactor)
```

Filter to only activated data sets.

```{r}
count_table_bound <- count_table_bound[,!(colData_bound$Activation %in% c('non-act', 'Act_and_p38i'))]
colData_bound <- colData_bound[!(colData_bound$Activation %in% c('non-act', 'Act_and_p38i')),]
```

Create DESeq data set.

```{r}
dds_act_merged <- DESeqDataSetFromMatrix(countData = count_table_bound,
                                         colData = colData_bound,
                                         design = ~ Experiment + Knockout)

rowData(dds_act_merged)$EnsemblID <- rownames(count_table_bound)
dds_act_merged <- dds_act_merged[rowSums(counts(dds_act_merged)) > 10, ] # remove <= 10 counts = noise
dds_act_merged <- reannotate(dds_act_merged)
```

Run DESeq itself.

```{r}
dds_act_merged <- DESeq(dds_act_merged)
```
Get r-log-normalized data.

```{r}
rlog_act_merged <- rlog(dds_act_merged, blind = FALSE)
```

Now we can make PCA. We plot PCA for 1-2 and 2-3 components. We include blank versions without text for easier manipulation.

```{r}
pca_data_cmp <- get.complete.PCA.data(rlog_act_merged)
pca_data <- pca_data_cmp$x %>% as.data.frame %>% cbind(., colData(dds_act_merged))

# get fraction of variability captured by each PC
pca_Var <- pca_data_cmp$sdev^2/sum(pca_data_cmp$sdev^2)
```

```{r}
pca1 <- ggplot(pca_data, aes(x = PC1, y = PC2, color = Knockout, shape = Batch)) +
  geom_point(size = 5) +
  geom_text_repel(aes(label = rownames(pca_data)), col='black', seed = 120) +
  scale_color_manual(values = c(col_GTKO, col_WT)) +
  ggtitle(paste0('exp1+exp2 merge - Normalized PCA (design-aware, PC1 + PC2)' )) +
  xlab(paste0("PC1: ", round(pca_Var[1]*100), "% variance")) +
  ylab(paste0("PC2: ", round(pca_Var[2]*100), "% variance")) +
  theme_classic() +
  theme(panel.grid.major = element_line(colour = "grey70", size = 0.3),
        panel.grid.minor = element_line(colour = "grey70", size = 0.1))
print(pca1)

pca2 <- ggplot(pca_data, aes(x = PC2, y = PC3, color = Knockout, shape = Batch)) +
  geom_point(size = 5) +
  geom_text_repel(aes(label = rownames(pca_data)), col='black', seed = 120) +
  scale_color_manual(values = c(col_GTKO, col_WT)) +
  ggtitle(paste0('exp1+exp2 merge - Normalized PCA (design-aware, PC2 + PC3)' )) +
  xlab(paste0("PC2: ", round(pca_Var[2]*100), "% variance")) +
  ylab(paste0("PC3: ", round(pca_Var[3]*100), "% variance")) +
  theme_classic() +
  theme(panel.grid.major = element_line(colour = "grey70", size = 0.3),
        panel.grid.minor = element_line(colour = "grey70", size = 0.1))
print(pca2)
```

```{r}
tiff('Figures/NFkB_Figures/exp_merged_PCA1_PCA2.tiff', units = 'in', width = 7.5, height = 5.5, res = 150)
print(pca1)
dev.off()

tiff('Figures/NFkB_Figures/exp_merged_PCA2_PCA3.tiff', units = 'in', width = 7.5, height = 5.5, res = 150)
print(pca2)
dev.off()
```

Get contrast GTKO vs. WT.

```{r}
res_exp_act_merged <- lfcShrink(dds = dds_act_merged, contrast = c('Knockout', 'GTKO', 'WT'), type = 'ashr')
```

Make ranked list from contrast.

```{r}
ranked_exp_merged_act <- res_exp_act_merged$log2FoldChange
names(ranked_exp_merged_act) <- rownames(res_exp_act_merged)
```

Now do GSEA.

```{r, include = F}
set.seed(42)
fgsea_exp_merged_act <- fgsea(pathways = NFkB_target_genes,
                        stats = ranked_exp_merged_act,
                        nperm=500000)
```

Plot GSEA for all clusters.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I3']], ranked_exp_merged_act)$data

xcoord <- max(GSE_data$x) * 0.15
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.4 + min(GSE_data$y)
ycoord2 <- yrange * 0.3 + min(GSE_data$y)
ycoord3 <- yrange * 0.2 + min(GSE_data$y) 
  
GSEA_nfkb_6_I3 <- plotEnrichment(NFkB_target_genes[['I3']],
               ranked_exp_merged_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp_merged_act$padj[3], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp_merged_act$NES[3], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp_merged_act$size[3]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I3 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT Mice (Exp1+Exp2, act)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_6_I3)
```

```{r}
tiff('Figures/NFkB_Figures/exp_merged_act_NFkB_I3_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_6_I3)
dev.off()
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I1']], ranked_exp_merged_act)$data

xcoord <- max(GSE_data$x) * 0.15
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.4 + min(GSE_data$y)
ycoord2 <- yrange * 0.3 + min(GSE_data$y)
ycoord3 <- yrange * 0.2 + min(GSE_data$y) 
  
GSEA_nfkb_6_I1 <- plotEnrichment(NFkB_target_genes[['I1']],
               ranked_exp_merged_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp_merged_act$padj[1], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp_merged_act$NES[1], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp_merged_act$size[1]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I1 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT Mice (Exp1+Exp2, act)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_6_I1)
```

```{r}
tiff('Figures/NFkB_Figures/exp_merged_act_NFkB_I1_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_6_I1)
dev.off()
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I2']], ranked_exp_merged_act)$data

xcoord <- max(GSE_data$x) * 0.15
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.4 + min(GSE_data$y)
ycoord2 <- yrange * 0.3 + min(GSE_data$y)
ycoord3 <- yrange * 0.2 + min(GSE_data$y) 
  
GSEA_nfkb_6_I2 <- plotEnrichment(NFkB_target_genes[['I2']],
               ranked_exp_merged_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp_merged_act$padj[2], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp_merged_act$NES[2], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp_merged_act$size[2]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I2 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT Mice (Exp1+Exp2, act)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_6_I2)
```

```{r}
tiff('Figures/NFkB_Figures/exp_merged_act_NFkB_I2_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_6_I2)
dev.off()
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I6']], ranked_exp_merged_act)$data

xcoord <- max(GSE_data$x) * 0.15
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.4 + min(GSE_data$y)
ycoord2 <- yrange * 0.3 + min(GSE_data$y)
ycoord3 <- yrange * 0.2 + min(GSE_data$y) 
  
GSEA_nfkb_6_I6 <- plotEnrichment(NFkB_target_genes[['I6']],
               ranked_exp_merged_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp_merged_act$padj[4], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp_merged_act$NES[4], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp_merged_act$size[4]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I6 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT Mice (Exp1+Exp2, act)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_6_I6)
```

```{r}
tiff('Figures/NFkB_Figures/exp_merged_act_NFkB_I6_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_6_I6)
dev.off()
```

Make heatmap for combined data of select genes.
  
```{r, fig.width=8, fig.height=20}
colfunc <- colorRampPalette(c('steelblue', "gray90", 'firebrick'))
vis_genes <- intersect(NFkB_target_genes[['I3']], rownames(rlog_act_merged))
vis_genes_tab <- limma::removeBatchEffect(assay(rlog_act_merged)[vis_genes,], colData(rlog_act_merged)$Experiment)
vis_genes_tab <- vis_genes_tab[,c(1:6, 16:18, 7:15)]

pheatmap(vis_genes_tab, border = 'NA', scale = 'row', color=colfunc(64), cluster_rows = T,
         annotation_col = as.data.frame(colData(dds_act_merged)[c('Activation', 'Knockout', 'Batch')]), cluster_cols = F,
         main='Heatmap of NF-kB target genes between GTKO \n and WT, Activated and Inhibited mice (Exp2)', cex = 1,
         annotation_colors = list(Knockout = c(GTKO = col_GTKO, WT = col_WT)))
```

```{r, fig.width=8, fig.height=20}
colfunc <- colorRampPalette(c('steelblue', "gray90", 'firebrick'))
vis_genes <- intersect(NFkB_target_genes[['I1']], rownames(rlog_act_merged))
vis_genes_tab <- limma::removeBatchEffect(assay(rlog_act_merged)[vis_genes,], colData(rlog_act_merged)$Experiment)
vis_genes_tab <- vis_genes_tab[,c(1:6, 16:18, 7:15)]

pheatmap(vis_genes_tab, border = 'NA', scale = 'row', color=colfunc(64), cluster_rows = T,
         annotation_col = as.data.frame(colData(dds_act_merged)[c('Activation', 'Knockout', 'Batch')]), cluster_cols = F,
         main='Heatmap of NF-kB target genes between GTKO \n and WT, Activated and Inhibited mice (Exp2)', cex = 1,
         annotation_colors = list(Knockout = c(GTKO = col_GTKO, WT = col_WT)))
```

```{r, fig.width=8, fig.height=20}
colfunc <- colorRampPalette(c('steelblue', "gray90", 'firebrick'))
vis_genes <- intersect(NFkB_target_genes[['I2']], rownames(rlog_act_merged))
vis_genes_tab <- limma::removeBatchEffect(assay(rlog_act_merged)[vis_genes,], colData(rlog_act_merged)$Experiment)
vis_genes_tab <- vis_genes_tab[,c(1:6, 16:18, 7:15)]

pheatmap(vis_genes_tab, border = 'NA', scale = 'row', color=colfunc(64), cluster_rows = T,
         annotation_col = as.data.frame(colData(dds_act_merged)[c('Activation', 'Knockout', 'Batch')]), cluster_cols = F,
         main='Heatmap of NF-kB target genes between GTKO \n and WT, Activated and Inhibited mice (Exp2)', cex = 1,
         annotation_colors = list(Knockout = c(GTKO = col_GTKO, WT = col_WT)))
```

```{r, fig.width=8, fig.height=20}
colfunc <- colorRampPalette(c('steelblue', "gray90", 'firebrick'))
vis_genes <- intersect(NFkB_target_genes[['I6']], rownames(rlog_act_merged))
vis_genes_tab <- limma::removeBatchEffect(assay(rlog_act_merged)[vis_genes,], colData(rlog_act_merged)$Experiment)
vis_genes_tab <- vis_genes_tab[,c(1:6, 16:18, 7:15)]

pheatmap(vis_genes_tab, border = 'NA', scale = 'row', color=colfunc(64), cluster_rows = T,
         annotation_col = as.data.frame(colData(dds_act_merged)[c('Activation', 'Knockout', 'Batch')]), cluster_cols = F,
         main='Heatmap of NF-kB target genes between GTKO \n and WT, Activated and Inhibited mice (Exp2)', cex = 1,
         annotation_colors = list(Knockout = c(GTKO = col_GTKO, WT = col_WT)))
```

