---
title: "GSE analysis based on list of genes directly regulated by NF-kB"
author: "Juraj Michalik"
date: "2023-12-08"
output: html_document
---

LICENCE: MIT (see LICENCE.md)

Supplementary analysis using data (notably NF-kB target genes) from this paper: https://www.nature.com/articles/s41590-023-01561-7#Sec28

# Setup

Load required packages.

```{r, include = F}
knitr::opts_chunk$set(echo = FALSE)

library(DESeq2)
library(dplyr)
library(tibble)
library(ggrepel)
library(magrittr)
library(clusterProfiler)
library(fgsea)
library(pheatmap)
library(dichromat)
library(limma)
library(DT)

# annotation libs
library(AnnotationHub)

dir.create(file.path('GSEA_tables/'), showWarnings = F)

col_WT <- '#55a0fbff'
col_GTKO <- '#c000c0ff'
```

Function for reannotation and PCA.

```{r}
# Get current Mus Musculus database from AnnotationHub if not downloaded already
getEnsMm106 <- function(){
  aHu <- AnnotationHub()
  aHuQuery <- query(aHu, pattern = c("Mus Musculus", "EnsDb", '106'))
  EnsMm106 <- aHuQuery[[1]]
  return(EnsMm106)
}

# adds annotation to object
reannotate <- function(dds.obj, keyslist = row.names(dds.obj)){
  EnsMm106 <- getEnsMm106()
  symbol.vector <- mapIds(EnsMm106,
                          keys = row.names(dds.obj),
                          column = "SYMBOL",
                          keytype = "GENEID",
                          multiVals = "first")
  # rename only if symbol is a thing
  row.names(dds.obj) <- ifelse(is.na(symbol.vector) | symbol.vector == '', row.names(dds.obj), symbol.vector)
  return(dds.obj)    
}

# returns PCA data with more PCs (12 I think)
get.complete.PCA.data <- function(dds.obj, ntop = 500){
	rvar <- rowVars(assay(dds.obj))
	select <- order(rvar, decreasing=TRUE)[seq_len(min(ntop, length(rvar)))]
	pca.dat <- prcomp(t(assay(dds.obj)[select,]))
	return(pca.dat)
}
```

# GSEA tests

Here we will perform GSEA analysis on set of genes that are target for NFkB from the paper above. For this purpose we load required genes first. Note that some symbols from paper were replaced by equivalent used in Ensembl.

```{r}
NFkB_target_genes_I1 <- read.csv('Paper_I1_cluster.csv', h=T)[,1]

NFkB_target_genes_I2 <- read.csv('Paper_I2_cluster.csv', h=T)[,1]

NFkB_target_genes_I3 <- read.csv('Paper_I3_cluster.csv', h=T)[,1]

NFkB_target_genes_I6 <- read.csv('Paper_I6_cluster.csv', h=T)[,1]

NFkB_target_genes <- list(NFkB_target_genes_I1, NFkB_target_genes_I2, NFkB_target_genes_I3, NFkB_target_genes_I6)
names(NFkB_target_genes) <- c('I1', 'I2', 'I3', 'I6')
```

Create directory where pictures will be stored.

```{r}
dir.create(file.path('Figures/NFkB_Figures_Finalized'), showWarnings = F)
```

# Analysis

First we need to calculate contrast for exp1 between activated and non-activated cells because we don't have that from previous case. We therefore load counts and create new DESeq2 object. We also use slightly different design where we unify 1ku1 and 4ku1 for 1/1 4/1 ratios of activation beads (which were previously defined as separate levels).

```{r}
expcounts_1 <- readRDS('Rds_data/exp1_counts.rds')
expcounts_1$Activation.bin <- ifelse(expcounts_1$Activation == 'non-act', 'non-act', 'act')

dds_exp1_alt <- DESeqDataSet(expcounts_1, design = ~ Experiment + Activation.bin + Knockout)
rowData(dds_exp1_alt)$EnsemblID <- rownames(expcounts_1)
dds_exp1_alt <- dds_exp1_alt[rowSums(counts(dds_exp1_alt)) > 10, ] # remove <= 10 counts = noise
dds_exp1_alt <- reannotate(dds_exp1_alt)
```

Run DESeq.

```{r}
dds_exp1_alt <- DESeq(dds_exp1_alt)
```

Run DESeq, then get results for 'activated' vs. 'non-activated contrast'.

```{r}
res_exp1_act_vs_non_act <- lfcShrink(dds = dds_exp1_alt, contrast = c('Activation.bin', 'act', 'non-act'), type = 'ashr')
```

Now load previously completed results for comparison of GTKO vs. WT for activated data only.

```{r}
res_exp1_act_KO_vs_WT <- readRDS('Rds_data/exp1_res_KO_vs_WT_act_only.rds')
```

Make ranked list for each.

```{r}
ranked_exp1_all <- res_exp1_act_vs_non_act$log2FoldChange
names(ranked_exp1_all) <- rownames(res_exp1_act_vs_non_act)

ranked_exp1_act <- res_exp1_act_KO_vs_WT$log2FoldChange
names(ranked_exp1_act) <- rownames(res_exp1_act_KO_vs_WT)

ranked_exp1_all <- sort(ranked_exp1_all, decreasing = T)
ranked_exp1_act <- sort(ranked_exp1_act, decreasing = T)
```

Now do GSEA.

```{r, include = F}
set.seed(42)
fgsea_exp1_all <- fgsea(pathways = NFkB_target_genes,
                        stats = ranked_exp1_all,
                        nperm=500000)

fgsea_exp1_act <- fgsea(pathways = NFkB_target_genes,
                        stats = ranked_exp1_act,
                        nperm=500000)

```

Plot all for cluster I3 first.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I3']], ranked_exp1_all)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_1_I3 <- plotEnrichment(NFkB_target_genes[['I3']],
               ranked_exp1_all) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_all$padj[3], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_all$NES[3], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ',fgsea_exp1_all$size[3]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I3 cluster (direct target of NF-kB)\n for contrast of Activated vs. Non-Activated - Mice (Exp1, all)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_1_I3)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I3']], ranked_exp1_act)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_2_I3 <- plotEnrichment(NFkB_target_genes[['I3']],
               ranked_exp1_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_act$padj[3], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_act$NES[3], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp1_act$size[3]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I3 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT - Mice (Exp1, activ. only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_2_I3)
```

Save all of the above.

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_all_NFkB_I3_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_1_I3)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_act_NFkB_I3_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_2_I3)
dev.off()
```

Make blank variants.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}
GSEA_nfkb_1_I3_blank <- plotEnrichment(NFkB_target_genes[['I3']],
               ranked_exp1_all) + 
  ggtitle('\n') +
  theme_classic() + 
  xlab('') + ylab('') +
  theme(axis.text.x=element_blank(),
        axis.text.y=element_blank())

print(GSEA_nfkb_1_I3_blank)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}
GSEA_nfkb_2_I3_blank <- plotEnrichment(NFkB_target_genes[['I3']],
               ranked_exp1_act) + 
  ggtitle('\n') +
  theme_classic() + 
  xlab('') + ylab('') +
  theme(axis.text.x=element_blank(),
        axis.text.y=element_blank())

print(GSEA_nfkb_2_I3_blank)
```

Save those as well.

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_all_NFkB_I3_GSEA_blank.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_1_I3_blank)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_act_NFkB_I3_GSEA_blank.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_2_I3_blank)
dev.off()
```

Now do this for clusters I1, I2 and I6. I1 first.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I1']], ranked_exp1_all)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_1_I1 <- plotEnrichment(NFkB_target_genes[['I1']],
               ranked_exp1_all) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_all$padj[1], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_all$NES[1], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ',fgsea_exp1_all$size[1]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I1 cluster (direct target of NF-kB)\n for contrast of Activated vs. Non-Activated - Mice (Exp1, all)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_1_I1)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I1']], ranked_exp1_act)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_2_I1 <- plotEnrichment(NFkB_target_genes[['I1']],
               ranked_exp1_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_act$padj[1], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_act$NES[1], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp1_act$size[1]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I1 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT - Mice (Exp1, activ. only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_2_I1)
```

Save all of the above.

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_all_NFkB_I1_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_1_I1)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_act_NFkB_I1_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_2_I1)
dev.off()
```

Make blank variants.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}
GSEA_nfkb_1_I1_blank <- plotEnrichment(NFkB_target_genes[['I1']],
               ranked_exp1_all) + 
  ggtitle('\n') +
  theme_classic() + 
  xlab('') + ylab('') +
  theme(axis.text.x=element_blank(),
        axis.text.y=element_blank())

print(GSEA_nfkb_1_I1_blank)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}
GSEA_nfkb_2_I1_blank <- plotEnrichment(NFkB_target_genes[['I1']],
               ranked_exp1_act) + 
  ggtitle('\n') +
  theme_classic() + 
  xlab('') + ylab('') +
  theme(axis.text.x=element_blank(),
        axis.text.y=element_blank())

print(GSEA_nfkb_2_I1_blank)
```

Save those as well.

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_all_NFkB_I1_GSEA_blank.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_1_I1_blank)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_act_NFkB_I1_GSEA_blank.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_2_I1_blank)
dev.off()
```

Cluster I2.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I2']], ranked_exp1_all)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_1_I2 <- plotEnrichment(NFkB_target_genes[['I2']],
               ranked_exp1_all) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_all$padj[2], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_all$NES[2], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ',fgsea_exp1_all$size[2]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I2 cluster (direct target of NF-kB)\n for contrast of Activated vs. Non-Activated - Mice (Exp1, all)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_1_I2)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I2']], ranked_exp1_act)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_2_I2 <- plotEnrichment(NFkB_target_genes[['I2']],
               ranked_exp1_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_act$padj[2], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_act$NES[2], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp1_act$size[2]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I2 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT - Mice (Exp1, activ. only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_2_I2)
```

Save all of the above.

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_all_NFkB_I2_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_1_I2)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_act_NFkB_I2_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_2_I2)
dev.off()
```

Make blank variants.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}
GSEA_nfkb_1_I2_blank <- plotEnrichment(NFkB_target_genes[['I2']],
               ranked_exp1_all) + 
  ggtitle('\n') +
  theme_classic() + 
  xlab('') + ylab('') +
  theme(axis.text.x=element_blank(),
        axis.text.y=element_blank())

print(GSEA_nfkb_1_I2_blank)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}
GSEA_nfkb_2_I2_blank <- plotEnrichment(NFkB_target_genes[['I2']],
               ranked_exp1_act) + 
  ggtitle('\n') +
  theme_classic() + 
  xlab('') + ylab('') +
  theme(axis.text.x=element_blank(),
        axis.text.y=element_blank())

print(GSEA_nfkb_2_I2_blank)
```

Save those as well.

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_all_NFkB_I2_GSEA_blank.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_1_I2_blank)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_act_NFkB_I2_GSEA_blank.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_2_I2_blank)
dev.off()
```

Cluster I6.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I6']], ranked_exp1_all)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_1_I6 <- plotEnrichment(NFkB_target_genes[['I6']],
               ranked_exp1_all) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_all$padj[4], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_all$NES[4], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ',fgsea_exp1_all$size[4]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I6 cluster (direct target of NF-kB)\n for contrast of Activated vs. Non-Activated - Mice (Exp1, all)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_1_I6)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}

GSE_data <- plotEnrichment(NFkB_target_genes[['I6']], ranked_exp1_act)$data

xcoord <- max(GSE_data$x) * 0.55
yrange <- max(GSE_data$y) - min(GSE_data$y)
ycoord1 <- yrange * 0.9 + min(GSE_data$y)
ycoord2 <- yrange * 0.8 + min(GSE_data$y)
ycoord3 <- yrange * 0.7 + min(GSE_data$y) 
  
GSEA_nfkb_2_I6 <- plotEnrichment(NFkB_target_genes[['I6']],
               ranked_exp1_act) + 
  annotate("text", label = paste('padj = ', round(fgsea_exp1_act$padj[4], 6)), x = xcoord, y = ycoord1, size = 7, hjust = 0, col = 'firebrick2') +
  annotate("text", label = paste('NES = ', round(fgsea_exp1_act$NES[4], 6)), x = xcoord, y = ycoord2, size = 7, hjust = 0, col = 'firebrick3') +
  annotate("text", label = paste('Number of genes: ', fgsea_exp1_act$size[4]), x = xcoord, y = ycoord3, size = 7, hjust = 0, col = 'firebrick4') +
  ggtitle('GSEA of gene set from I6 cluster (direct target of NF-kB)\n for contrast of GTKO vs. WT - Mice (Exp1, activ. only)') +
  theme_classic() + 
  theme(plot.title = element_text(face="bold", hjust = 0.5))

print(GSEA_nfkb_2_I6)
```

Save all of the above.

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_all_NFkB_I6_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_1_I6)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_act_NFkB_I6_GSEA.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_2_I6)
dev.off()
```

Make blank variants.

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}
GSEA_nfkb_1_I6_blank <- plotEnrichment(NFkB_target_genes[['I6']],
               ranked_exp1_all) + 
  ggtitle('\n') +
  theme_classic() + 
  xlab('') + ylab('') +
  theme(axis.text.x=element_blank(),
        axis.text.y=element_blank())

print(GSEA_nfkb_1_I6_blank)
```

```{r, fig.width = 9, fig.show= 'hold', fig.align = 'center'}
GSEA_nfkb_2_I6_blank <- plotEnrichment(NFkB_target_genes[['I6']],
               ranked_exp1_act) + 
  ggtitle('\n') +
  theme_classic() + 
  xlab('') + ylab('') +
  theme(axis.text.x=element_blank(),
        axis.text.y=element_blank())

print(GSEA_nfkb_2_I6_blank)
```

Save those as well.

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_all_NFkB_I6_GSEA_blank.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_1_I6_blank)
dev.off()
```

```{r}
tiff('Figures/NFkB_Figures_Finalized/exp1_act_NFkB_I6_GSEA_blank.tiff', units = 'in', width = 7.5, height = 4.5, res = 150)
print(GSEA_nfkb_2_I6_blank)
dev.off()
```

Save RDS of DESeq2 object.

```{r}
saveRDS(dds_exp1_alt, 'Rds_data/exp1_DESeq_all_alt_design.rds')
```
